### 2017-11-02 manuscript.rmd
look at all trees
added phylogenetic signal and AIC code

@@

>>>>

	# Uncomment for development to look at a subset of gene trees
	# gene_trees = gene_trees[1:100]

@@

#### Model selection and sensitivity

```{r phylogenetic_signal, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

	k_thresh = quantile( tree_summary$K, na.rm=TRUE )[3] # third quantile is the median
	k_percentile = names(k_thresh)
	genes_pass_k = tree_summary$gene[ tree_summary$K > k_thresh ]

	nodes_contrast_filtered_k = 
		nodes_contrast %>% 
			filter( gene %in% genes_pass_k )

	wilcox_test_result_k = wilcox_oc( nodes_contrast_filtered_k )

We removed the `r k_percentile` of genes with the lowest phylogenetic signal, corresponding to a K cutoff for retained genes of greater than `r signif( k_thresh, 3)`. Repeating the phylogenetic analyses on this subset of genes with strongest phylogenetic signal for Tau still do not reject the null hypothesis (Wilcoxon p = $`r  wilcox_test_result_k %>% round( 3 )`$).

```{r model_selection, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

	dAIC_thresh = 2
	AIC_min = pmin( tree_summary$aic_bm, tree_summary$aic_ou )
	tree_summary$dAIC = tree_summary$aic_ou - tree_summary$aic_bm
	tree_summary$dAIC_bm = tree_summary$aic_bm - AIC_min
	tree_summary$dAIC_ou = tree_summary$aic_ou - AIC_min
	genes_pass_bm = tree_summary$gene[ tree_summary$dAIC_bm < dAIC_thresh ]
	genes_pass_ou = tree_summary$gene[ tree_summary$dAIC_ou < dAIC_thresh ]

	nodes_contrast_filtered_bm = 
		nodes_contrast %>% 
			filter( gene %in% genes_pass_bm )

	wilcox_test_result_bm = wilcox_oc( nodes_contrast_filtered_bm )

Of the `r nrow(tree_summary)` genes considered, and a $\Delta$AIC threshold of `r dAIC_thresh`, `r sum(tree_summary$dAIC_bm < dAIC_thresh & tree_summary$dAIC_ou >= dAIC_thresh)` have $\Delta$AIC less than the threshold only for Brownian Motion (BM), `r sum(tree_summary$dAIC_bm >= dAIC_thresh & tree_summary$dAIC_ou < dAIC_thresh)` have $\Delta$AIC less than the threshold only for Ornstein Uhlenbeck (OU), and `r sum(tree_summary$dAIC_bm < dAIC_thresh & tree_summary$dAIC_ou < dAIC_thresh)` have $\Delta$AIC less than the threshold for both models. That gives a total of `r sum( tree_summary$dAIC_bm < dAIC_thresh )` genes that have $\Delta$AIC less than the threshold for BM and `r sum( tree_summary$dAIC_ou < dAIC_thresh )` genes that have $\Delta$AIC less than the threshold for OU.

Repeating the BM phylogenetic analyses on the subset of `r sum( tree_summary$dAIC_bm < dAIC_thresh )` genes that have $\Delta$AIC less than the threshold for BM still does not reject the null hypothesis (Wilcoxon p = $`r  wilcox_test_result_bm %>% round( 3 )`$).

```{r model_ou, cache=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

	# Get the trees that pass AIC criteria for OU
	gene_trees_pic_digests = lapply( gene_trees_pic, digest )
	gene_trees_pic_ou = gene_trees_pic[ gene_trees_pic_digests %in% genes_pass_ou ]

	# Replace the BM pics with OU pics
	gene_trees_pic_ou %<>% add_pics_to_trees( model_method="OU" )
	nodes_ou_contrast = gene_trees_pic_ou %>% summarize_contrasts()
	wilcox_ou = wilcox_oc( nodes_ou_contrast )
